An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-11-03 tex/paper.tex
References to more tournaments

\begin{table}[!hbtp]
    \begin{center}
        \begin{tabular}{ccccc}
            \toprule
            Year     & Reference           & Number of Strategies & Type     & Source Code\\
            \midrule
            1979     & \cite{Axelrod1980a} & 13                   & Standard & Not immediately available\\
            1979     & \cite{Axelrod1980b} & 64                   & Standard & Not immediately available\\
            1991     & \cite{Bendor1991}   & 13                   & Noisy    & Not immediately available\\
            2002     & \cite{Stephens2002} & 16                   & Wildlife & Not applicable\\
            % Is this worth including? If so I think we need more.
            \bottomrule
        \end{tabular}
    \end{center}
    \caption{An overview of published tournaments}\label{tab:tournaments}
\end{table}

>>>>

\begin{table}[!hbtp]
    \begin{center}
        \begin{tabular}{ccccc}
            \toprule
            Year     & Reference           & Number of Strategies & Type     & Source Code\\
            \midrule
            1979     & \cite{Axelrod1980a} & 13                   & Standard & Not immediately available\\
            1979     & \cite{Axelrod1980b} & 64                   & Standard & Available in FORTRAN\\
            1991     & \cite{Bendor1991}   & 13                   & Noisy    & Not immediately available\\
            2002     & \cite{Stephens2002} & 16                   & Wildlife & Not applicable\\
            2005     & \cite{kendall2007iterated} & 223           & Varied   & Not available \\
            2012     & \cite{Stewart2012} & 13                    & Standard & Not fully available \\
            \bottomrule
        \end{tabular}
    \end{center}
    \caption{An overview of published tournaments}\label{tab:tournaments}
\end{table}
